Sound Automated Synthesis of Digital Controllers

### 2016-10-12 paper/paper.tex
revised general CEGIS description to go with the new figure

\paragraph{General architecture of the program synthesiser}
%
%% \red{[I would recommend to clarify the domain of definition of $\sigma$, particularly over the set where $x$ ranges over. 
%% (Be cognisant that control audience might be unfamiliar with the cegis architecture.) ]}
% 
The input specification provided to the program synthesiser is of the
form $\exists \vec{P} . \forall \vec{x} \in \text{\sc inputs}
. \sigma(\vec{x}, \vec{P})$ where $\vec{P}$ ranges over functions,
$\vec{x}$ ranges over ground terms and $\sigma$ is a quantifier-free
formula.  We interpret the ground terms over some finite domain
$\mathcal{D}$.

The design of our synthesiser is given in Fig.~\ref{fig:CEGIS} and
consists of two phases, {\sc Synthesise} and {\sc Verify}, which
interact via a finite set of test vectors {\sc inputs} that is updated
incrementally.  Given the aforementioned specification $\sigma$, the
{\sc synth} procedure tries to find an existential witness $\vec{P}$
satisfying the specification $\sigma(\vec{x}, \vec{P})$ for all
$\vec{x}$.
%
If {\sc synthesise} succeeds in finding an witness $\vec{P}$, this
witness is a candidate solution to the full synthesis formula.  We
pass this candidate solution to {\sc verify}, which determines whether
it does satisfy the specification on all inputs by checking
satisfiability of the following verification formula:
%
$\exists \vec{x} . \lnot \sigma(\vec{x}, \vec{P})$

If this formula is unsatisfiable, the candidate solution is in fact a
solution to the synthesis formula and so the algorithm terminates.
Otherwise, the witness $\vec{x}$ denote an input on which the
candidate solution fails to meet the specification.  Thus, $\vec{x}$ is
added to the {\sc inputs} set, and the loop iterates again.  It is
worth noting that each iteration of the loop adds a new input to the
finite set $\text{\sc inputs}$ being used for synthesis.  Given that
the full set of inputs $\mathcal{D}$
%\blue{[which by now should have a name, as suggested to be introduced above]} 
is finite, this means that the refinement loop
can only iterate a finite number of times.

>>>>

\paragraph{General architecture of the program synthesiser}
%
%% \red{[I would recommend to clarify the domain of definition of $\sigma$, particularly over the set where $x$ ranges over. 
%% (Be cognisant that control audience might be unfamiliar with the cegis architecture.) ]}
% 
The input specification provided to the program synthesiser is of the
form $\exists \vec{P} . \forall \vec{x}. \sigma(\vec{x}, \vec{P})$ where $\vec{P}$ ranges over functions,
$\vec{x}$ ranges over ground terms and $\sigma$ is a quantifier-free
formula.  We interpret the ground terms over some domain
$\mathcal{D}$.

The design of our synthesiser is given in Fig.~\ref{fig:CEGIS} and
consists of two phases, {\sc Synthesise} and {\sc Verify}, which
interact via a finite set of test vectors {\sc inputs} that is updated
incrementally.  Given the aforementioned specification $\sigma$, the
{\sc synth} procedure tries to find an existential witness $\vec{P}$
satisfying the specification $\sigma(\vec{x}, \vec{P})$ for all
$\vec{x}$ in {\sc inputs} (as opposed to all $\vec{x} \in \mathcal{D}$).
%
If {\sc synthesise} succeeds in finding an witness $\vec{P}$, this
witness is a candidate solution to the full synthesis formula. 
We pass this candidate solution to {\sc verify}, which 
checks whether it is a full solution.
%determines whether
%it does satisfy the specification on all inputs by checking
%satisfiability of the following verification formula:
%
%$\exists \vec{x} . \lnot \sigma(\vec{x}, \vec{P})$
%If this formula is unsatisfiable, 
%% the candidate solution is in fact a 
%% full solution.
If this is the case, then
the algorithm terminates.
Otherwise, additional information is provided to the {\sc synthesise}
phase (e.g. a new counterexample that is added to the {\sc inputs} set)
and the loop iterates again.

%% the witness $\vec{x}$ denote an input on which the
%% candidate solution fails to meet the specification.  Thus, $\vec{x}$ is
%% added to the {\sc inputs} set, and the loop iterates again.

%% It is
%% worth noting that each iteration of the loop adds a new input to the
%% finite set $\text{\sc inputs}$ being used for synthesis.  Given that
%% the full set of inputs $\mathcal{D}$
%% %\blue{[which by now should have a name, as suggested to be introduced above]} 
%% is finite, this means that the refinement loop
%% can only iterate a finite number of times.
